Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-10 pecomplexity.tex
moving things

\begin{enumerate}
\item \cmark~Introduce MASE.
\item \cmark~WPE is a good measure of predictability.  Figure: best athlete MASE vs.
its WPE.
\item \cmark~Talk about structure analysis. Just because there is forward information
transfer, does not mean that linear predictors can get at this.
\item For this show a figure of (a) ARIMA vs MASE (b) LMA vs MASE in a side by
side plot.
\item full results.  Image: MASE vs. WPE for both LMA \& ARIMA.  Points to make:
\begin{enumerate}
\item \cmark~clusters are distributed differently
\item \cmark~clusters are shaped differently---tight or not
\item \cmark~clusters move differently between LMA and ARIMA
\item finally, the diagonal line is important. If you're below it, you could do
better.
\end{enumerate}
\end{enumerate}

>>>>

OUTLINE:
\begin{enumerate}
\item \cmark~Introduce MASE.
\item \cmark~WPE is a good measure of predictability.  Figure: best athlete MASE vs.
its WPE.
\item \cmark~Talk about structure analysis. Just because there is forward information
transfer, does not mean that linear predictors can get at this.
\subitem \cmark~For this show a figure of (a) ARIMA vs MASE (b) LMA vs MASE in a side by
side plot.
\item full results.  Image: MASE vs. WPE for both LMA \& ARIMA.  Points to make:
\begin{enumerate}
\item \cmark~clusters are distributed differently
\item \cmark~clusters are shaped differently---tight or not
\item \cmark~clusters move differently between LMA and ARIMA
\item finally, the diagonal line is important. If you're below it, you could do
better.
\end{enumerate}
\end{enumerate}

In this section we will validate the two key findings of this work:

[[Rephrase these]]
\begin{enumerate}

\item The existence of complex structure in a noisy real-valued time series is quantifiable and this type of complexity is directly correlated with predictability

\item The way structure/information/complexity is processed internally by a given process plays a role in predictability.
